---
title: "A Spatial Analysis of the IUCN Status of Global Marine Fish"
author: "Faúndez-Baez, P., Hartline, N., Mayorga-Henao, J., Villaseñor-Derbez, J.C."
date: "March 10, 2016"
output: 
  ioslides_presentation:
  #  fig_width: 1
  #  fig_height: 1
  #  fig_caption: true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Algo

##Maping mariculture variables

```{r, warning=FALSE}

setwd("~/KUNI/KUNI-Mariculture.github.io")

suppressPackageStartupMessages({
  library(readr)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(knitr)
  library(shiny)
  library(googleVis)
  
  library(devtools)
#library(fish.ecol)
library(networkD3)
library(data.tree)

})

```

## Otro
```{r, TaxApp, output="asis", message=FALSE}
require(shiny)
data1 <- read_csv('maps/data/data_normalized_092616.csv')
data2 <- read_csv('maps/data/CountryConversion.csv')
data3 <- merge(x = data1, y=data2, by.x = c("country"), by.y=c("FAO_Country"))
data3 <- data3[!is.na(data3$gdp),]

gdp <- data3$gdp
FAO_Country <- data3$country

  ui <- shinyUI(fluidPage(
  
  # Application title
  titlePanel("pal que lee"),
  
  # Show a plot of the generated distribution
  mainPanel(
    htmlOutput("gvis")
  )
))


server <- shinyServer(function(input, output) {
  
  output$gvis=renderGvis({
    
    temp <- data.frame(data = gdp, FAO_Country = FAO_Country) 
    # Plot countries
    
    gvisGeoChart(temp, "FAO_Country", "data", hovervar="FAO_Country",
                 options=list(gvis.editor="gdp", colorAxis="{colors:['#FFFFFF', '#0000FF']}"))
    
    
  })
})


shinyApp(ui = ui, server = server)
 
 ## <- the function ends!!
```
